\section{Untrusted App on Benign OS}
\label{sec:problem2}

In this section, we discuss the protection of the operating system from an
untrusted application or a piece of untrusted code. In this paper, we call both
of untrusted application and untrusted code as untrusted module. The untrusted
module can be pieces of native code downloaded by a web browser, an application
uploaded and executed on the PaaS server, or an Android application downloaded
from an untrusted third part. Although the isolation of untrusted module can
prevent it from infecting the operating system, it is far from enough. There are
other challenges. First, the isolated code module wants to interact with the
operating system services via system calls. Second, the isolation (sandbox)
should not impact the performance of program execution. Third, a low
implementation overhead is expected, that is, the modification to compiler,
linker, application source code and operating system kernel source code should
be minimized. Last, since the smartphone has limited resources, the isolation
should be lightweight. 

In this paper, we categorize the prior works according to the granularity of
isolation. The granularity of isolation varies, including intro-process,
inter-process, inter-namespace and inter-VM. 

\begin{table*}[ht]
	\centering
	\begin{tabular}{|l|l|}
		\hline
		\textbf{Solution Category}      & \textbf{Research Papers} \\ \hline
		Inter-VM Based         & KVM/ARM \cite{KVM/ARM} \\ \hline
		Intra-Process Based    & SFI \cite{SFI}, PittSFIeld \cite{PittSFIeld}, Native Client \cite{NaCl} \\ \hline
		Inter-Process Based    & Native Client \cite{NaCl}, Krude \etal \cite{Krude} \\ \hline
		Inter-Namespace Based  & TrustDroid \cite{TrustDroid}, Cells \cite{Cells}, AirBag \cite{AirBag} \\ \hline	
	\end{tabular}
	\caption{Solution categorization on the protection of OS from the untrusted
	application.}
	\label{my-label}
\end{table*}

\subsection{Inter-VM based}
\label{sec:problem2:inter-vm}

The naive approach is to isolate each untrusted module into its correpsonding
VM. There are a variety of virtual machine monitors, including Xen, KVM, Qemu,
and VMWare.  Recently, the hardware virtualization extension has been added into
the ARM and the ARM based KVM \cite{KVM/ARM} is integrated into the Linux kernel
since Linux 3.9. Since this approach is clear and self-explained, we will not
discuss it in detail in this paper.

\subsection{Intra-Process based}
\label{sec:problem2:intra-process}

Intra-Process protection is to isolate the untrusted module from the other
memory regions in the same address space. SFI \cite{SFI} is proposed to sandbox
the untrusted module by rewriting the untrusted code at the instruction level,
that is, to instrument store/load and control flow instructions. However, it
only works for RISC architectures. PittSFIeld \cite{PittSFIeld} presents
sandboxing technique that can be applied to CISC architecture e.g. IA-32, and
whose application can be checked at load-time to minimize the TCB.  Unlike RISC
architectures, whose instructions have the same length, the x86 has
variable-length instructions that might start at any byte. To avoid this
problem, PittSFIeld divides memory into segments whose size and location is
16-byte aligned.  New instructions are instrumented before store/load and
control flow instructions to check that the sandboxed module cannot read/write
data outside sandbox and transfer to illegal control flow target outside
sandbox.

A weakness of PittSFIeld is it cannot effectively mediate the access from
untrusted module to operating system services. Besides isolating the untrusted
module, Native Client \cite{NaCl} also allows the module to interact
with services, such as file I/O and local database access, by the combination of
intra-process and inter-process approaches.  An Intra-Process based sandbox is
used to isolate the untrusted module from the runtime service, which resides in
the same address space as the sandboxed untrusted module. Runtime service
mediates the communication between the untrusted module and other processes
including web browser and other services. This is similar to the Inter-Process
based solution in the next section.

\subsection{Inter-Process based}
\label{sec:problem2:inter-process}

Krude \etal \cite{Krude} is an inter-process based isolation approach to sandbox
the untrusted module. It is specifically designed for PaaS architectures, where
code execution needs to be isolated to protect tenants from unauthorized access
to their data by other tenants and to protect the host system from any type of
intrusion by other tenants. The untrusted module is uploaded to the PaaS server
and it is isolated in a new process. Krude \etal uses the process barrier and
the seccomp filter mechanism to restrict access to memory and to the system call
interface. Almost all system calls are blocked for the isolated process. Besides
memory allocation and deallocation, the isolate can communicate with OS by
sending to request to a supervisor process via pipe, which is the IPC mechanism
on Linux. The supervisor process will process the request and send the response
back to the isolated process also via pipe.

\subsection{Inter-Namespace based}
\label{sec:problem2:inter-namespace}

The Inter-Namespace based approach is primary proposed for smartphone running
Android. Nowadays, smartphones are ubiquitous. Many use the smartphone both for
working and personal needs. However, the personal applications downloaded from
the untrusted website can compromise the application issued by the trusted
enterprise. Therefore, many users carry multiple phones to accommodate work,
personal and geographic mobility need. Cells proposes a smartphone
virtualization solution so that multiple virtual smartphones can run
simultaneously on the same physical smartphone in an isolated, secure manner.
Unlike the virtualization techniques mentioned in section
\ref{sec:problem2:inter-vm}, Cells leverages a lightweight OS-level
virtualization by the utilization of namespace. Linux namespace is being used by
OpenVZ and LXC. A set of processes can be grouped into the same namespace. Each
Linux namespace has PID namespace isolation, network namespace isolation, UTS
namespace isolation, mount namespace islation and IPC namespace isolation.

Cells observes that smartphones display only a single application at a time, and
introduces a usage model which has one foreground Virtual Phone (VP) that is
displayed and multiple background VPs that are not displayed at any given time.
The foreground VP is always given direct access to hardware devices while the
back ground VPs are given shared access to hardware devices when the foreground
VP does not require exclusive access. Cells provides novel kernel-level and
user-level device namespace mechanisms to efficiently multiplex hardware devices
across multiple VPs. Therefore, untrusted application inside personal VP
(namespace) will not be able to compromise the trusted application inside
enterprise VP. 

While Cells aims to embrace the emerging Bring-Your-Own-Device (BYOD) paradigm,
each VP is treated equally and the isolation is achieved at the coarse-grained
VP boundary. Unlike Cells, AirBag \cite{AirBag}'s objective is to boost the
smartphone's defense capability against the malware infection by isolating the
untrusted application in the AirBag environment. By dynamically creating an
isolated runtime environment with its own dedicated namespace and virtualized
system resources, AirBag is able to protect the OS from the malicious untrusted
applications, e.g., an Android game repacked with the malware. AirBag creates
and decouples an Application Isolation Runtime (AIR) from the native Android
runtime, which contains Java \& Native Libraries, Application framework (e.g.,
SurfaceFlinger service) and Dalvik virtual machine.  AIR does not need to be
trusted as it might be potentially compromised by untrusted application. AirBag
multiplexes hardware resources between the AIR and native runtime by either
creating a second resource (e.g., memory buffer) or creating a proxy between
runtimes and hardware to mediate access from different runtimes.



